XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler

### 2024-11-05 paper/main.tex
Update main.tex: related works - generative information extraction
generative information extraction

\subsection{LLMs and Webpage Content Simplification}
An alternative approach to direct information extraction involves simplifying web content through LLMs before targeting specific data points. This method filters out redundant HTML elements, reducing the size and complexity of web data while retaining the relevant information for extraction. By employing techniques such as chunking and semantic classification, LLMs like those used in RAG models can focus on high-value segments, improving processing efficiency (Ahluwalia \& Wani, 2024) Studies have shown that simplifying web pages using LLMs significantly enhances their performance in dynamic environments, especially when dealing with varied and noisy HTML structures (Deng et al., 2023). Moreover, this approach aligns with efforts to reduce the cognitive load on models, particularly in contexts requiring rapid, scalable information extraction (Sàrl and Godin, 2023).

>>>>

\subsection{Generative Information Extraction}
The use of large models for information extraction is commonly referred to as generative information extraction, which leverages large language models (LLMs) to extract structured knowledge from text, such as entities, relations, and events, providing an alternative to traditional discriminative methods (Xu et al., 2024). Unlike traditional models, LLMs directly generate structured information and perform well even in low-resource settings, supporting multitasking formats. IE tasks are generally categorized into Named Entity Recognition (NER), Relation Extraction (RE), and Event Extraction (EE), with each task's performance and typical models rigorously compared (Xu et al., 2024). Recent universal IE frameworks employ both natural language-based (NL-LLMs) and code-based (Code-LLMs) approaches. NL-LLMs, such as UIE and InstructUIE, use natural language prompts to generate structured information, whereas Code-LLMs, like Code4UIE and CodeKGC, utilize code-based schemas for more precise knowledge representation (Gan et al., 2023; Wei et al., 2023; Bi et al., 2024).
